Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-08-05 paper/icse23.tex
m

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{comment}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\newcommand{\timedEffects}{\emph{TimEffs}}
\newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}}
\newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
\newcommand{\timedL}{\code{C^{t}}}
\newcommand{\anyevent}[1]{{\textcolor{darkred}
{{\textbf{\small #1}}}}}
\newcommand{\anynotevent}[1]{{\textcolor{darkred}
{{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
\newcommand{\code}[1]{{\tt{\ensuremath{\m{#1}}}}}
\newcommand{\codeme}[1]{{\tt{\ensuremath{#1}}}}
\newcommand{\CONTAIN}{\sqsubseteq}
\newcommand{\underscore}{\textcolor{vividauburn}{\code{\_}}}
\newcommand{\m}{\mathit} 
\newcommand{\lappend}{\mathrel{\texttt{++}}}

\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}

\newcommand\theoref[1]{Theorem~\textcolor{blue}{\ref{#1}}}
\newcommand\lemmaref[1]{Lemma~\textcolor{blue}{\ref{#1}}}
\newcommand\appref[1]{Appendix~\textcolor{blue}{\ref{#1}}}
\newcommand\defref[1]{Definition~\textcolor{blue}{\ref{#1}}}
\newcommand\algoref[1]{Algorithm~\textcolor{blue}{\ref{#1}}}

@@

\begin{comment}
\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}
\end{comment}

\maketitle

\begin{abstract}
    The correctness of real-time systems 
    depends both on the correct functionalities and the realtime constraints.
    To go beyond the existing Timed Automata based techniques, 
    we propose a novel solution that integrates a 
    modular Hoare-style forward verifier with a new term rewriting 
    system (TRS) on \emph{Timed Effects} (\timedEffects).
    The main purposes are to increase the expressiveness,  
    dynamically create clocks, 
    and efficiently solve constraints on the clocks.  
    We formally define 
    a core language \timedL, generalizing the real-time systems, modeled 
    using mutable variables and timed behavioral patterns, 
    such as \emph{delay}, \emph{timeout}, \emph{interrupt}, \emph{deadline}. 
    Secondly, to capture real-time specifications, 
    we introduce \timedEffects, a new effects logic, 
    that extends 
    \emph{Regular Expressions} with dependent
    values and arithmetic constraints.
    Thirdly,  the forward verifier infers temporal behaviors of given 
    \timedL\ programs, expressed in \timedEffects. 
    Lastly, we present a purely algebraic TRS, i.e., an extended \emph{Antimirov algorithm}, to 
    efficiently prove language inclusions between 
     \timedEffects. 
    To demonstrate the feasibility of our proposals, 
    we prototype the verification system; prove its 
    soundness; report on case studies and the experimental results.     
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.

%%
%% If your work has an appendix, this is the place to put it.
\appendix

>>>>

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage[numbers]{natbib}
\usepackage{filecontents}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{stmaryrd}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newtheorem{definition}{Definition}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{varwidth}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\anynotevent}[1]{{\textcolor{darkred}
{{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
\newcommand{\env}{\code{\mathcal{V}}}
\newcommand{\es}{\theta}
\newcommand{\ev}{ev}
\newcommand{\siderule}[1]{
\code{\footnotesize{\textcolor{mGray}{#1}}}}
\usepackage{adjustbox}
\usepackage{ebproof}
\usepackage{cancel}
\newcommand{\CONTAIN}{\sqsubseteq}
\definecolor{mypink}{RGB}{219, 48, 122}
\definecolor{darklavender}{rgb}{0.45, 0.31, 0.59}
\definecolor{deepcerise}{rgb}{0.85, 0.2, 0.53}
\def\defeq{\ensuremath{\,\triangleq}}
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
\newcommand{\anyevent}[1]{{\textcolor{darkred}
{{\textbf{\small #1}}}}}
\newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}}
\newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
\newcommand{\timedL}{\code{C^{t}}}

\newcommand\theoref[1]{Theorem~\textcolor{blue}{\ref{#1}}}
\newcommand\lemmaref[1]{Lemma~\textcolor{blue}{\ref{#1}}}
\newcommand\appref[1]{Appendix~\textcolor{blue}{\ref{#1}}}
\newcommand\defref[1]{Definition~\textcolor{blue}{\ref{#1}}}
\newcommand\algoref[1]{Algorithm~\textcolor{blue}{\ref{#1}}}
\newcommand{\code}[1]{{\tt{\ensuremath{\m{#1}}}}}
\newcommand{\m}{\mathit} 
\newcommand{\lappend}{\mathrel{\texttt{++}}}
\definecolor{mGray}{rgb}{0.4,0.4,0.4}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{huntergreen}{rgb}{0.33, 0.42, 0.18}

\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
\newcommand{\timedEffects}{\emph{TimEffs}}
\usepackage{wrapfig}
\newcommand{\effect}{{\ensuremath{\mathrm{\Phi}}}}
\usepackage{listings}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, void, const, new, int, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean,event, timeout, deadline, delay,  throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{darklavender}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstset{
   language=JavaScript,
   %%backgroundcolor=\color{lightgray},
   extendedchars=true,
   basicstyle=\footnotesize\ttfamily,
   showstringspaces=false,
   showspaces=false,
%frame=single
numbers=left,   
xleftmargin=1em, 
    numberstyle=\tiny\color{mGray},
   numbersep=10pt,
   tabsize=4,
   breaklines=true,
   showtabs=false,
   captionpos=b,
   keywordstyle=[2]\color{purple}\bfseries, %
   morekeywords=[2]{do, hiphop,every, loop,suspend, when, signal, end, present, nothing, emit,in, out, yield,abort, fork, par, run},
}

@@

\begin{comment}
\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}
\end{comment}
\pagestyle{plain}
\maketitle

\begin{abstract}
    The correctness of real-time systems 
    depends both on the correct functionalities and the realtime constraints.
    To go beyond the existing Timed Automata based techniques, 
    we propose a novel solution that integrates a 
    modular Hoare-style forward verifier with a new term rewriting 
    system (TRS) on \emph{Timed Effects} (\timedEffects).
    The main purposes are to increase the expressiveness,  
    dynamically create clocks, 
    and efficiently solve constraints on the clocks.  
    We formally define 
    a core language \timedL, generalizing the real-time systems, modeled 
    using mutable variables and timed behavioral patterns, 
    such as \emph{delay}, \emph{timeout}, \emph{interrupt}, \emph{deadline}. 
    Secondly, to capture real-time specifications, 
    we introduce \timedEffects, a new effects logic, 
    that extends 
    \emph{Regular Expressions} with dependent
    values and arithmetic constraints.
    Thirdly,  the forward verifier infers temporal behaviors of given 
    \timedL\ programs, expressed in \timedEffects. 
    Lastly, we present a purely algebraic TRS, i.e., an extended \emph{Antimirov algorithm}, to 
    efficiently prove language inclusions between 
     \timedEffects. 
    To demonstrate the feasibility of our proposals, 
    we prototype the verification system; prove its 
    soundness; report on case studies and the experimental results.

\end{abstract}

\begin{IEEEkeywords}
    Temporal Verification,
    Dependant Effects,
    Hoare-style Forward Verifier,
    Term Rewriting System,
    Timed Verification
\end{IEEEkeywords}

\section{Introduction}
\label{Introduction}

Specification and verification of real-time systems are essential 
to research topics with practical implications. During the last 
more than two decades, a popular approach for specifying real-time systems has been 
based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
Timed Automata are powerful 
in designing real-time models with explicit clock variables. Real-time 
constraints are captured by explicitly setting/resetting clock variables. 
A number of automatic verification support for Timed Automata have proven 
to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.

Models based on Timed Automata often adopt a simple structure, e.g., a 
network with no hierarchy. The benefit is that 
efficient model checking is made feasible. Nonetheless, designing and 
verifying compositional real-time systems is becoming an increasingly 
difficult task due to the widespread applications and increasing complexity 
of such systems. In industrial case studies of real-time system verification, system 
requirements are often structured into phases, which are then composed 
sequentially, in parallel and alternatively \cite{DBLP:conf/emsoft/LarsenMNS05}. 
Unlike timed process algebras, Timed Automata lack high-level 
compositional patterns for hierarchical design. As a result, users often 
need to manually cast those terms into a set of clock variables with 
carefully calculated clock constraints. The process is tedious and error-prone.

We investigate an alternative approach for modeling and verifying 
compositional real-time systems. In this work, 
we propose a novel temporal specification language, 
which enables a compositional verification via a  Hoare-style 
forward verifier and a term rewriting system (TRS). 
More specifically, we specify system behaviors in the form of 
{Timed Effects} (\timedEffects), which integrates the Kleene Algebra 
with dependent values and arithmetic constraints, 
%gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
to 
%capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
provide real-time abstractions into traditional linear temporal logics. 
%Resource usages, provided by a \emph{dynamic ticks}\cite{DBLP:conf/fdl/HanxledenBG17}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
For example, one safety property, \textit{"The event \anyevent{Done} 
will be triggered no later than one time unit"}\footnote{Without loss of generality, 
we use integer values to represent time units in this 
paper.% while it can bes extended to real numbers and other 
%time measurement units.
}, is expressed in \timedEffects\ as: 
\begin{align*}
  \code{\effect \defeq \  0 {\leq} t {<}1 \wedge ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}
\end{align*}  
%The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
%and .
%which replaces temporal operators by time-constrained versions from 
Here, \code \wedge  connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
constraints for the \emph{logical-time} sequences \cite{DBLP:conf/fdl/HanxledenBG17}; 
\code{\_} is a wildcard matching to any event; 
Kleene star \code{\star} denotes trace repetition.
The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1)}\ }\anyevent{Done}' 
in metric temporal logic (MTL), reads \textit{"within one second, 
\anyevent{Done} finally happens"}.

Moreover, the time bounds 
can be dependent on the program inputs, demonstrated in 
\figref{fig:Value_dependent_intro}; we mark the precondition and postcondition
using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.

\begin{wrapfigure}{L}{0.39\columnwidth}
\begin{lstlisting}[name=coffee]
void addOneSugar() 
/*req: true/\ _^*
  ens: t>1 /\ emp#t */ 
{ timeout ((), 1); }

void addNSugar (int n) 
/*req: true/\ _^*
  ens: d>=n/\ Sugar#d */
{ if (n == 0) { 
      event ["Sugar"];} 
  else {
      addOneSugar();
      addNSugar (n-1);}} 
\end{lstlisting}
\caption{Value-dependent specification.} 
\label{fig:Value_dependent_intro}
\vspace{0mm}
\end{wrapfigure}

The function \code{addNSugar} takes a parameter \code{n}, representing 
the portion of the sugar we need to add. When \code{n} 
equals to \code{0}, 
it simply raises an event \anyevent{Sugar} to mark the end of the process. 
Otherwise, it adds one portion of the sugar by calling
\code{addOneSugar()}, then recursively calls 
\code{addNSugar} with parameter \code{n-1}. 
The use of statement \lstinline|timeout(e, d)| is standard \cite{JSTO}, 
which executes a block of code \code{e} after the specified time \code{d}.
Therefore, the time spent on adding one portion of the sugar is 
no less than one time unit. Note that {\color{darklavender}\code{\emph{emp\#t}}} 
refers to an empty trace which takes time \code{t}.

Both preconditions require no arithmetic constraints,   
and  have no temporal constraints upon 
the history traces. 
The postcondition of \code{addNSugar(n)} indicates that  the method 
generates a finite trace where \anyevent{Sugar} takes a no 
less 
than \code{d} time-units delay to finish.

Although these examples are simple, they show the benefits of deploying 
value-dependent 
time bounds, which is beyond the capability of Timed Automata. Intuitively, if traditional Timed Automata define an 
\emph{exact} transition system, \timedEffects\ define 
a set (possibly infinite) of exact transition systems.

Moreover, we deploy a Hoare-style forward verifier to 
soundly infer the actual behaviors of given programs 
concerning the well-defined operational semantics. 
This approach provides a 
\emph{direct} (opposite to the techniques which require 
 manual and remote modeling processes), 
  and modular compositional 
verification for real-time systems, which are not possible
by existing techniques.

\begin{comment}
  we express, the effects of \code{addNSugar(d)} as:
\begin{align*}
&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
\end{align*}  
effects of \code{addNSugar(n)} as:
\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}

\end{comment}

   %they already illustrate the gain of expressiveness from  existing temporal logics and traditional Timed Automata.

%properties

Having \timedEffects\ to be  the specification language, 
and the forward verifier to infer the program behaviors, 
we are interested 
in the following verification problem: 
Given a program \code{\mathcal{P}},
and a temporal specification \code{\effect^{\prime}}, does the inclusions 
\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds\footnote{The 
inclusion relation $\CONTAIN$ is formally defined in \defref{Inclusion}.}? Typically, 
checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.

Since the expressiveness of \timedEffects\ goes beyond 
finite-state automata, it is neither sufficient nor efficient to 
translate them 
into Timed Automata and reply on the solving engines of Timed Automata.
Therefore we 
develop a novel TRS, 
which  is inspired by Antimirov and Mosses’ algorithm\footnote{Antimirov and Mosses' 
algorithm was designed for deciding the inequalities of regular 
expressions based on an 
complete 
axiomatic algorithm of the algebra of regular sets.} \cite{DBLP:journals/tcs/AntimirovM95} but solving the 
language inclusions between more expressive \timedEffects.

\begin{comment}
  several compositional ,  
are introduced to capture quantitative timing constraints.
The idea is to

In this work, we study temporal verification of 
compositional real-time systems,

Existing automatic verification techniques massively rely on 
the Timed Automata which requires manually cast of clock variables with 
carefully calculated clock constraints.

A TRS is a refutation method that normalizes expressions in such a way 
that checking their inclusion corresponds to an iterated process of 
checking the inclusion of their \emph{partial derivatives} 
\cite{antimirov1995partial}. 
Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.

This work targets timed temporal verification, and to the best of 
the authors' knowledge, it proposes the first algebraic TRS 
 for the real-time verification. 
\end{comment}

 In short, the main contributions of this work are:

\begin{enumerate}
\item \textbf{Language Abstraction:} we formally define 
a core language \timedL, by defining its syntax and operational semantics, 
generalizing the real-time systems with mutable variables and timed 
behavioral patterns. %, such as \emph{delay}, \emph{timeout}, \emph{deadline}.

\item \textbf{Specification Language:} we propose \timedEffects, 
by defining its 
syntax and semantics, gaining the expressive power beyond 
traditional modeling languages for real-time systems.

\item \textbf{Automated Forward Verifier:} we establish a sound axiomatic 
semantics to infer the 
temporal behaviors of given target programs.  The verifier triggers the back-end 
solver TRS.

\item \textbf{An Efficient TRS:}
we present the rewriting rules to prove the inclusion relations between the inferred 
behaviors and the given temporal specifications, both in  \timedEffects.

\item \textbf{Implementation and Evaluation:} we prototype the novel 
effects logic and the automated verification system, 
prove the soundness, report on case studies and experimental results.

\end{enumerate}

\section{Overview}\label{sec:Overview}

We now highlight our main methodologies, using the example shown 
in \figref{fig:overview_coffee} This example simulates a 
coffee machine, which dynamically adds sugar based on the user's input number.

%\subsection{HipHop.js and Dependent Effects}
\subsection{\timedEffects}
As shown in \figref{fig:overview_coffee}, we define Hoare-triple 
style specifications (enclosed in 
\textcolor{darklavender}{\ttfamily{{/* ... */}}}) for each function, 
which leads to a compositional verification strategy, where static 
checking and timed temporal verification can be done locally.

%columns=fullflexible
\begin{wrapfigure}{L}{0.47\columnwidth}
  %\vspace{-1mm}
\begin{lstlisting}[name=coffee]
void makeCoffee (int n)
/*req: n>=0 /\ _^* . Cup
  ens: (n<=t<=5 /\ t1<=3) /\
       (Sugar#t).(Coffee#t1) */
{ deadline (addNSugar(n), 5);
  deadline (event["Coffee"], 3);}

int main ()
/*req: true/\emp
  ens: t<=8/\(((!Done)^*)#t).Done */ 
{ event["Cup"];
  makeCoffee (3);
  event["Done"];}
\end{lstlisting}  
   %   \vspace{-1mm}
\caption{To make coffee with three portions of sugar 
within eight time units.}\label{fig:overview_coffee}
 %        \vspace{0mm}
\end{wrapfigure}

The precondition of \code{makeCoffee} 
 specifies that the input integer value \code{n} is non-negative, and it requires that before entering into this 
function, this history trace must contain the event  
\anyevent{Cup} on the tail. Therefore, function calls to \code{makeCoffee} which 
do not satisfy the precondition lead to a failure of the verification. 
\code{makeCoffee} sets a 
five time-units deadline while calling 
\code{addNSugar} (defined in 
Fig. \textcolor{black}{\ref{fig:Value_dependent_intro}}),
 with argument \code{n}; then emits event \anyevent{Coffee} with
 a three time-units deadline.

The precondition of \code{main} requires no arithmetic constraints 
on its inputs (expressed as \code{true}) and 
an empty history trace (denoted using \code{emp} or \code{\epsilon}).
The postcondition of \code{main} specifies 
that before the final \anyevent{Done} happens, there is no 
occurrence of \anyevent{Done} (\code{!A} refers to the 
negation of the event \code{A}). Moreover, the whole process takes 
no more than eight time-units to hit the final event.

\timedEffects\ supports more features such as \emph{disjunctions}, 
\emph{guards} and \emph{parallelism}, etc., which can be found in 
\secref{subsec:Specification_language} and 
\secref{subsec:Specification_Semantics}.  
Note that directly from the specifications, we are aware of:  
(i) the branching properties: different arithmetic conditions on the input parameters lead to different temporal effects;
and (ii) the required history traces: by defining the prior effects 
in precondition. 
The examples 
already show that our  effects provide more detailed information than 
traditional timed verification, and in fact, it cannot be fully 
captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
Nevertheless, the gain in expressive power comes from the efforts 
of a more dedicated verification process, handled by our forward verifier and TRS.

\subsection{Forward Verification}
As shown in \figref{fig:forward_example}, we demonstrate the 
forward verification process of the functions \code{addOneSugar} and   {\code{addNSugar}}.
The current effects states are captured 
in the form of 
\code{\{ \textcolor{darklavender}{\effect_C} \}}. 
To facilitate the illustration, we label the verification 
steps by (1), ..., (11), and mark the deployed inference 
rules (cf. \secref{Forward_Rules}) in \textcolor{mGray}{[gray]}.
The verifier invokes the TRS to check language inclusions along the way.

\begin{comment}

/*require n>=0, _^*
  ensure  t>=n, Sugar#t */
{

\end{comment}

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {%\small
         \begin{enumerate}
\item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}.}} \\
\textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
\quad \siderule{\scriptsize[FV\text{-}Meth] } \\

\item ~\qquad \lstinline|timeout ((), 1);}| \\
\textcolor{darklavender}{\code{\effect_C^\prime {=} t_0{>}1   \wedge \_^\star \cdot \epsilon \mysharp t_0  }} 
\quad \siderule {\scriptsize [FV\text{-}Timeout]}
\item 
\textcolor{darkred}{\code{
%\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
\effect_C^\prime \CONTAIN \effect_{pre}^{addOneSugar(n)} \cdot \effect_{post}^{addOneSugar(n)} \Leftrightarrow  }} 
 %\textcolor{mGray}{  \emph{(-- check postcondition --) }}
 \textcolor{darkred}{\code{\code{\code{t_0{>}1   \wedge \epsilon \mysharp t_0}
 \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
 \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked. }}
 \\ 
%ens: t>1 /\ emp#t */ { 
  \noindent\rule{0.92\columnwidth}{0.4pt}
  \vspace{2mm}
~\\
\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize 
\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addNSugar(n)}}.}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  true \wedge  \_^\star \} }} 
      \quad \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} 
     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge   \_^\star \cdot Sugar\} }} 
     \quad \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0 \wedge   \_^\star \}  }} 
     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
    \item 
     ~\qquad~\qquad \lstinline|addOneSugar();| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0 \wedge  t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} 
     \quad \siderule {\scriptsize [FV\text{-}Call]}
     \item 
     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0   \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
      \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: precondition checked.}}
\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
     \quad \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }} 
      \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
      %\quad \siderule {\scriptsize [Normalization]}
      \\
       \item 
       %\textcolor{mGray}{  \emph{(-TRS: check the  postcondition; Succeed, cf. \autoref{tab:rewriting_tree_send}-) }}\\
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}  
       \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked, cf. \tabref{tab:rewriting_tree_send}. }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\

\end{enumerate}}

     \end{minipage}

      \caption{The forward verification example for method \code{send}. }\label{fig:forward_example}
     % \vspace{-4mm}
\end{figure}
}

The effects states (1) and (4) are obtained by initializing 
\code{\effect_C} from the precondition, by the \code{[FV\text{-}Meth]} rule. 
The effects states (5), (7), and (10) are obtained by  
\code{[FV\text{-}If\text{-}Else]}, which adds the constraints 
from the conditionals into the current effects state, 
and unions the effects accumulated from two branches in the end. 
The effects states (6) is obtained by \code{[FV\text{-}Event]}, 
which concatenates the triggered singleton event to the 
end of the current effects state.

The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
Before each function call, it invokes the TRS to check whether the current effects state 
satisfies the precondition of the callee function. 
If it is not satisfied, the verification fails; otherwise, 
it concatenates the callee's postcondition to the current 
effects state (the precondition check for step (8) is omitted here).

The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
which adds a lower time-bound to the trace. 
After these states transformations, steps (3) and (11) check the 
satisfiability of the inferred effects against the declared 
postcondition by invoking the TRS.

Note that the prior effects in precondition are new regarding 
the existing real-time verification.

\subsection{The TRS}

Our TRS is 
%obligated to check the inclusions between \effectNameSyncEffs, which is 
an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{DBLP:journals/tcs/AntimirovM95}  
decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their 
\emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
$\code{[DISPROVE]}$, which infers false from trivially inconsistent inequalities; and  
$\code{[UNFOLD]}$, which applies \defref{RegularInclusion} to generate new inequalities.
In detail, given \code{\Sigma} is the whole set of the alphabet, 
\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the event \code{\anyevent{A}}.

\begin{definition}[REs Inequality]\label{RegularInclusion}  For REs \code{r} and \code{s}, \code{r \preceq s \Leftrightarrow \forall (\anyevent{A} \in \Sigma).\ D_{\anyevent{A}}(r) \preceq D_{\anyevent{A}}(s)}.
\end{definition}

\begin{definition}[\timedEffects\ Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
For \timedEffects\ \code{\effect_1 } and \code{\effect_2}, 
\code{\effect_1 { \CONTAIN} \effect_2 {\Leftrightarrow} \forall \anyevent{A}. \forall t {\geq} 0.\ D_{\anyevent{A} \mysharp  t}(\effect_1)  
{\CONTAIN} D_{\anyevent{A} \mysharp  t}(\effect_2)}.
\end{definition}
%\in fst(\effect_1)

Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  
between \timedEffects, where \code{D_{\anyevent{A}\mysharp  t}(\effect)} 
is the partial derivative of \code{\effect} w.r.t the event 
\anyevent{A} and the time variable \code{t}.

%Adapting to the context of checking inclusions between \timedEffects, we extend the Antimirov algorithm with

%The rule \code{[REOCCUR]} finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{DBLP:conf/tableaux/Brotherston05}. (We use \code{\textcolor{persianplum}{(\dagger)}} in \tabref{tab:rewriting_tree_send} to indicate such pairings.)

%(introduce \code{t_L^1} and \code{t_L^2}, let \code{t_L^1 {+} t_L^2 {=} t_L}

%(\code{\{Cook\} {\Rightarrow} \{Cook\}}, \code{t_L^1 {+} t_L^2 {<}3 {\Rightarrow} t_L^1 {<}3})

Next, we continue with the step (11) in \figref{fig:forward_example}, to 
demonstrate how the TRS handles arithmetic constraints and dependent values. 
%We use the postcondition proving for function \code{main} as an example to briefly demonstrate the rewriting process. 
As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
 satisfy the declared postcondition. 
%property \code{\effect_1  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\mysharp  t)\cdot\_^\star}, 
%where \code{\effect_1} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces. 
We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.

{
\begin{table*}[ht]
\centering
     % \vspace{0mm}
\caption{\label{tab:rewriting_tree_send} The inclusion proving example. 
\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}
